\chapter*{\centering Abstract}
Evaluating scholarly impact accurately is crucial for academic advancement, but traditional metrics
like the H-Index have limitations, particularly their susceptibility to inflation through
lower-quality publications.  This thesis proposes three novel H-Index variants—H5-Adjusted H-Index,
JIF-Adjusted H-Index, and EigenFactor-Adjusted H-Index—that incorporate journal quality metrics
and subject-specificity to provide a more accurate measure of scholarly impact.

Data was collected from the Crossref-2024 dataset, and subject classifications
were assigned using Scopus ASJC codes. The adjusted H-Indexes were calculated
by considering only publications in the top 20\% of journals within specific
subjects, based on their H5, JIF, and EigenFactor rankings. The implementation
involved SQL and ROLAP analysis, with additional calculations performed in
Python, and unit testing that ensured the accuracy and reliability of these
calculations.

The study found strong correlations between the traditional H-Index and the
adjusted H-Indexes, indicating that researchers who rank highly by traditional
metrics also rank highly when journal quality is considered. The analysis
revealed that authors publishing in lower-tier journals tend to cite less
influential research compared to those publishing in top-tier journals.
Additionally, citation network analysis showed that top authors in general are
part of more interconnected and influential research networks.

These findings suggest that incorporating journal quality into H-Index
calculations mitigates issues such as H-Index inflation and provides a more
nuanced assessment of scholarly impact. This approach benefits researchers,
practitioners, and policymakers by offering more equitable and accurate
academic evaluations. Finally, the study highlights the need for further
research into advanced H-Index variants and subject-specific citation patterns
to enhance bibliometric evaluations.
