\chapter{Comments}
\label{ch:comments}

\section{EY and the Work Environment}

Concerning the work environment at EY, I found it to be professional,
collaborative, and supportive. To start with, the company's main offices of are
located in Cheimara 8, Marousi, Athens, where most of the employees are based.
However, many consultants often work at clients' locations. The EY headquarters
in Greece feature an open-space design, with large tables that facilitate team
collaboration by allowing employees to sit close to each other and easily
change their workspace. Individuals from all levels of the hierarchy share the
same working area. Each employee is provided with a laptop and a monitor, which
can be connected to the laptop to create a dual-screen setup. The company also
provides employees with a headset for conference calls and online meetings. The
office is equipped with modern technology, including video conferencing
systems, projectors, and whiteboards, to facilitate communication and
collaboration among employees and teams.

The office environment is designed to be comfortable and conducive to
productivity, with ergonomic chairs and adjustable desks. There are also
breakout areas where employees can relax, socialize, or have informal meetings.
The office has a kitchen area with a coffee machine, a refrigerator, and a
microwave, where employees can prepare and store their meals. The company
provides coffee, tea, and snacks for employees. The office also has a wellness
room where employees can take a break, meditate, or relax. The office is
accessible by public transportation, with a bus stop nearby and a parking area
for employees who commute by car. The office hours are from 9:00 am to 5:30 pm,
with a one-hour lunch break. However, employees have the flexibility to adjust
their working hours to accommodate personal commitments or work requirements.
The company also offers remote working options, allowing employees to work from
home or other locations when necessary.

The office culture is friendly and inclusive, and employees are encouraged to
share their ideas and opinions. The company organizes team-building activities,
training sessions, and social events to foster a sense of community and
collaboration among employees. In my opinion, this work environment encourages
employees to collaborate and share their knowledge. The open-space architecture
made it easier for me to interact with others and adapt to the new setting.

My colleagues were enthusiastic about discussing the analytics applications
they had previously worked on, as well as new ideas. My manager was always
available to provide guidance and support, which helped me integrate into the
team quickly. I believe my team's culture was one of the most significant
benefits of my internship at Ernst \& Young. My manager and my colleague were
not only knowledgeable and kind but also always willing to share their
knowledge and experience with me, which helped me learn and grow
professionally. The project director, who was the overall supervisor of the
project, although not directly involved in the day-to-day activities, was a
great professional, humble and a great person, always willing to help and
provide guidance and support. This made the whole experience even more
enjoyable and rewarding, allowing us to deliver high-quality results and exceed
the project's objectives and the client's expectations. Lastly, In the
advantages of EY I would also add the possibility to work in various industries
and experience clients with different strategies. The challenge to adopt to
each one so as to provide high quality services within time and budget presents
genuine interest.

Overall, the workplace environment at Ernst \& Young is conducive to learning,
growth, and professional development and I consider the interaction with
motivated colleagues to be one of the main benefits of my internship.

\section{Afterthoughts}

Transitioning from university to a professional workplace takes time and
presents an interesting yet challenging change in a student's life. Each day
offers new lessons, where you learn from both your mistakes and insights. Soft
skills such as communication, teamwork, and flexibility are developed through
practice.

In addition to the soft skills I gained from daily routines, I also applied
knowledge from my studies to real-world problems. I realized that sometimes you
need to unlearn some habits that what you have previously learned to advance
further. A willingness to continuously learn is crucial for personal
development. EY supports this by providing online platforms for training, which
I utilized to explore new topics and reinforce existing knowledge, throughout
my internship.

In conclusion, I view the internship as a significant opportunity to learn
about oneself and apply the knowledge gained over four years of study. Through
a process of trial and error, I was able to develop my skills and gain
confidence in my abilities. The experience has been invaluable, and I am
grateful for the opportunity to work with such a talented and supportive team.