\chapter{Description}
\label{ch:description}

\section{Department}

% Info about the department
The Data \& AI Department of Ernst \& Young Greece is responsible for providing
data analytics and artificial intelligence services to clients. The department
is staffed with professionals with expertise in data science, machine learning,
and artificial intelligence. The department's services include data analysis,
data visualization, machine learning model development, and artificial
intelligence solutions. The department works with clients from various
industries, including primarily financial services, telecommunications, retail
and public sector organizations. Additionally, the department provides it
services to other sectors such as energy, utilities, and healthcare. The
department's goal is to help clients leverage their data to make informed
business decisions, improve operational efficiency, and drive innovation, by
not only providing data analytics and artificial intelligence solutions but
also by offering strategic advice on how to best utilize data and AI
technologies and offering valuable insights on how to implement data-driven
strategies, in order to help clients understand their data and make better
decisions.

The Data \& AI Department at Ernst \& Young Greece is structured to support its
diverse range of services and client needs. The department consists of
approximately 200 professionals and the Department is led by the Leading
Partner of the Data \& AI Department, Elias Vyzas, who oversees all activities
and ensures alignment. Following the Leading Partner, the department is leaded
by Directors, who are responsible for the overall strategy and operations of
the department along with the Senior Managers. Additionally, the department is
divided into several teams, each specializing in a specific project or service
area. The teams include a Manager and the team members, who are responsible for
the day-to-day operations and project delivery. Important to note is that a
manager and a team member can be part of multiple teams, depending on the
projects and the services that are provided to the clients.

\section{Position}

% Info about the position
The position I was assigned to during my internship at Ernst \& Young Greece
was that of a Data Scientist. As a Data Scientist, my role was to support the
Data \& AI Department in delivering data analytics and artificial intelligence
solutions to clients. My responsibilities included working on data analysis,
developing machine learning models, and creating data visualizations to help
clients understand their data and make informed decisions. Specifically, I was
involved in the Fulgor AI project, which aimed to develop an AI-powered
solution for predicting the quality of produced cable splices.

My responsibilities included collecting and preprocessing IoT time series data
from cable production processes. This involved cleaning the data, handling
missing values, and normalizing the data to prepare it for analysis. I worked
on extracting relevant features from the raw data to improve the accuracy of
the predictive models, identifying key indicators of cable coil quality, and
transforming the data into a suitable format for machine learning algorithms.
Moreover, I developed predictive models using anisotropic learning techniques
to analyze the time series data and predict the quality of the produced cable
splices. This involved experimenting with various machine learning algorithms,
such as Random Forest, Gradient Boosting, and Neural Networks, to determine the
most effective approach.

I evaluated the performance of the predictive models using metrics such as
accuracy, precision, recall, and F1-score. Based on the evaluation results, I
optimized the models by tuning hyperparameters and improving feature selection.
I created interactive data visualizations to present the findings and insights
from the predictive models to stakeholders. These visualizations helped clients
understand the factors affecting cable splice quality and make informed
decisions to improve production processes. I documented the methodologies,
procedures, and results of the project in detailed reports, including writing
technical documentation and creating presentations for both technical and
non-technical audiences. I also communicated regularly with clients to gather
requirements, provide updates, and deliver final solutions

\section{Required Skills}

% Info about the required skills
The position of Data Scientist at Ernst \& Young Greece required a combination
of technical and soft skills to successfully deliver data analytics and
artificial intelligence solutions to clients. The technical skills required for
the position included proficiency in programming languages such as Python, SQL
and scripting languages such as Bash, as well as experience with data analysis
libraries such as Pandas, NumPy, and Scikit-learn. Additionally, knowledge of
machine learning algorithms, data preprocessing techniques, and model
evaluation methods was essential for developing predictive models and analyzing
data effectively as well as experience with time series analysis and feature
extraction techniques. Furthermore, experience with deep learning frameworks
such as TensorFlow and Keras was required to develop advanced machine learning
models for complex data analysis tasks.

The position also required experience with data visualization tools such as
Matplotlib, Seaborn, and Plotly to create interactive visualizations and
present insights to stakeholders. Moreover, familiarity with cloud platforms
such as Azure experience with version control systems such as Git was also
required to manage code and collaborate with team members effectively.

In addition to technical skills, the position required strong analytical and
problem-solving skills to identify patterns, trends, and anomalies in data and
develop innovative solutions to complex business problems. Effective
communication skills were also essential for presenting findings to clients,
collaborating with team members, and documenting project methodologies and
results. Lastly, the position required the ability to work independently
and as part of a team, manage multiple tasks simultaneously, and adapt to
changing project requirements and priorities.



\section{Expected Results}

The expected results of my internship at Ernst \& Young Greece included
successfully completing the Fulgor AI project and delivering a high-quality
AI-powered solution for predicting the quality of produced cable coils to the
client. Apart from the technical deliverables, I also aimed to satisfy the
expectations of my supervisors and colleagues by demonstrating professionalism,
teamwork, and effective communication throughout the internship.