\chapter{Discussion and Implications}
\label{ch:discussion}

\section{Discussion of Results}

The results of the study show that the adjusted H-Indexes are significantly
correlated with the traditional H-Index, with correlation coefficients in the
range of 0.6 to 0.7. This indicates a strong positive relationship between the
traditional H-Index and the adjusted H-Indexes, suggesting that researchers who
rank highly according to the traditional H-Index also tend to rank highly
according to the adjusted H-Indexes.

However, compared to other H-Index variants, as reviewed in the literature, the
correlation is not perfect. This imperfection highlights the distinctiveness of
the adjusted H-Indexes. While the strong correlation signifies that the
adjusted H-Indexes retain the fundamental characteristics of the traditional
H-Index, the differences suggest that the adjustments made for journal quality
and subject specificity introduce meaningful variations. These variations
likely reflect the impact of publishing in higher-quality journals and the
influence of subject-specific citation practices, which are not captured by the
traditional H-Index, which

The adjusted H-Indexes reduce the number of authors with high H-Indexes
compared to the traditional H-Index, leading to disinflation of H-Index values
and potentially providing a more accurate representation of the authors'
scholarly impact. This is evident from the reduction in the number of authors
with H-Indexes above certain thresholds, as shown in Table
\ref{tab:thresholds}.

The analysis of citation practices reveals significant differences between
authors publishing in lower-tier journals and those in top-tier journals.
Authors from lower-tier journals have a significantly lower average h-index of
cited journals compared to random authors from top-tier journals, suggesting
that they cite less influential or lower-quality research. This pattern is
consistent across all subject areas, emphasizing the importance of journal
quality in citation practices and the impact on the overall scholarly
contribution of authors.

Furthermore, the citation network clustering analysis highlights that top
authors are more likely to be part of tightly-knit citation clusters. This
interconnectedness is particularly pronounced in fields like Life Sciences and
Multidisciplinary research, where collaboration is more prevalent. The higher
clustering coefficients for top authors suggest that the authors are more
engaged in collaborative research and are part of a more cohesive research
community, which may contribute to their higher scholarly impact.

These findings emphasize the need for incorporating journal quality and the
need for considering subject-specific citation network structures into
bibliometric evaluations. By doing so, we can achieve a more accurate and
comprehensive assessment of a researcher's true impact, beyond what the
traditional H-Index alone can offer. This approach helps to mitigate issues
such as H-Index inflation and not accounting for the quality of the journals in
which researchers publish along with the subject-specific citation practices,
and thus provides a clearer picture of scholarly contributions regardless of
the field of research.

\section{Implications for Researchers and Practitioners}

The findings of this study have several implications for researchers and
practitioners in the field of bibliometrics and research evaluation. First,
researchers should be aware of the limitations of traditional H-Index metrics
and consider the impact of journal quality on their scholarly impact. By
publishing in reputable journals with high impact factors and h-index values,
researchers can enhance the visibility and recognition of their work, leading
to a more accurate assessment of their scholarly impact. Researchers could also
modify the threshold of the journal quality metrics, such as the top 10\% or
top 30\% of journals, to further refine the adjusted H-Indexes and tailor them
to their specific research field, based on how strict they want to be in
considering the journal quality.

Practitioners involved in research evaluation and funding decisions should also
take into account the quality of the journals in which researchers publish when
assessing their impact. By incorporating journal quality metrics into
evaluation criteria, practitioners can ensure a more comprehensive and
meaningful evaluation of researchers' contributions to their field.

Furthermore, the study highlights the need for further research into more
nuanced H-Index variants that address issues such as self-citation and
hyperauthorship. By developing more sophisticated, but not complex to
calculate, H-Index metrics that provide a more refined measure of scholarly
impact, researchers and practitioners can improve the accuracy and fairness of
bibliometric evaluations.

Lastly, the study showcases a methodological approach to evaluating scholarly
impact metrics that incorporate journal quality and subject specificity into
the calculation of H-Indexes. Specifically, by using the Alexandria3k tool to
extract and analyze publication data from Crossref-2024, along with the
effective use of ROLAP analysis and testing, the study demonstrates a robust
and reliable method for calculating efficiently and accurately adjusted
H-Indexes. By adopting similar methodologies, researchers and practitioners can
enhance the reliability and validity of bibliometric evaluations along with the
assessment of scholarly impact and much more.

Overall, the study contributes to the ongoing discussion on the limitations of
traditional H-Index metrics and provides a more nuanced and accurate assessment
of scholarly impact by incorporating journal quality and subject specificity
into the evaluation criteria. By addressing these limitations and providing
insights into citation practices and patterns across different subject areas,
the study contributes to a more comprehensive understanding of scholarly impact
and research evaluation, ultimately benefiting researchers, practitioners, and
policymakers involved in academic assessments and funding decisions. %TODO: Check

%This thesis, by introducing a new metric that incorporates journal quality into
%the calculation of the H-Index, with different ways of ranking journals based
%on their quality, aims to address the limitations of the traditional H-Index
%and provide a more accurate and meaningful assessment of a researcher's
%scholarly. As such, the following research questions are posed: First, what is
%the correlation between traditional H-Index values and the proposed H-Index
%metrics that account for journal quality? Second, how do citation practices
%differ between top authors publishing in low-quality journals and authors
%publishing in high-quality journals. Third, how do citation patterns differ
%between hyperprolific researchers and regular researchers across different
%subject areas? By addressing these research questions, this thesis seeks not
%only to develop and validate improved H-Index calculations that incorporate
%journal quality, but to also provide insights into the citation practices and
%patterns of researchers across different subjects, thus contributing to a more
%complete understanding of scholarly impact.


% The study answers all the research questions and hypotheses, and the results
% show that the firstly, the incorporation of subject-specific journal rankings
% based on H5-Index, EigenFactor and Impact Factor significantly affects the
% H-Index calculation, as it takes into account the quality of the journals in
% which the researcher’s works are published, which in turn provides a more
% accurate and nuanced estimation of the researcher’s true impact. Secondly, the
% correlation between traditional H-Index values and the proposed H-Index metrics
% that account for journal quality is strong, indicating a positive relationship
% between the traditional H-Index and the adjusted H-Indexes. Finally, the
% citation patterns differ between researchers with high traditional H-Indexes
% and those with high proposed H-Indexes that incorporate journal quality,
% highlighting the influence of journal quality and subject specificity on
% scholarly impact metrics. 
